Elephant Seal Age JAE Intraspecific Variation

### 2023-12-01 paper/paperv2_old.qmd
Updating the paper with Roxanne's feedback

sealdat <- read_csv(here::here("data/raw/128L pull 2023_11_21.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1994)

@@

We also plotted survival bias to show that 95% of pups were resighted within 7 years. Both plots are supplemental.

@@

survival95 <- quantile(survival_bias$first_resight_yrs, 0.95)
#n for 95% quantile
sum(survival_bias$first_resight_yrs > 7)

>>>>

sealdat <- read_csv(here::here("data/raw/128L pull 2023_11_21.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  select(-c("tagsex", "season", "numbreed", "firstyearindicator", "indices")) %>% 
  filter(age > 3, 
         year > 1994)

@@

We also plotted survival bias to show that 95% of pups were resighted within 10 years. Both plots are supplemental.

@@

survival95 <- quantile(survival_bias$first_resight_yrs, 0.95)
#n for 95% quantile
sum(survival_bias$first_resight_yrs > 10)

### 2023-12-01 paper/paperv3.qmd
Updating the paper with Roxanne's feedback

```{r}
#| label: setup
#| include: false

library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(patchwork)

sealdat <- read_csv(here::here("data/raw/128L pull 2023_11_21.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1994)

@@

>>>>

```{r}
#| label: setup
#| include: false  
library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(patchwork)

sealdat <- read_csv(here::here("data/raw/128L pull 2023_11_30.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987)
```

@@

table(seal_phenology$age,seal_phenology$observed)
